
Burns has been the PI of five completed NSF-funded projects addressing high-performance data systems 
and scientific computing.   Award CCF-0937810 (12/15/09--12/14/13) developed throughput-oriented 
scheduling techniques for data-intensive clusters that preserve the performance of 
Web services when they scale out to support many users and large queries.  
The project resulted in four successive publications in the Supercomputing Conference from 2009--2013.
CAREER Award CCF-0238305 (5/1/03--4/30/08).  He was the PI of ``CAREER: Interoperation among Heterogeneous
Global-Scale Systems'' (NSF ACI-0238305, \$407,000, 3/15/03--3/14/08),  that built tools that manage the 
lifetime of data and allow information to flow seamlessly across management and software boundaries.  It lead
to more than 15 refereed conference and journal publications, including a Best Paper Award.

Burns has been the Co-PI of 7 interdisciplinary NSF grants that connect CISE and a science domain.
He has worked across turbulence with an ITR (2004-09) and two CDI awards (2010-2014,2015), 
astrophysics (2004-07, 2012-14, 2013-2018), and environmental engineering (2004-09).  He 
has had collaborative neuroscience funding since 2011 through the NIH and DARPA.

Burns has been PI for the joint NSF/NIH program Collaborative Research in Computational 
Neuroscience (NIBIB 1RO1EB016411-01).  Vogelstein was a Co-PI.  Burns and Vogelstein were
co-PIs on the joint NSF/NIH BIGDATA grant (NIDA 1R01DA036400-01).  

In addition, Vogelstein was PI for ``A Scientific Planning Workshop for Coordinating Brain Research Around the Globe''  (NSF, \$97,950, 04/01/2016 -- 03/31/2017), which coordinated the Global Brain Workshop 2016, from which these ideas emerged.  A perspective piece on the outcome of that meeting is currently under review at Science, and available from the workshop's website: \url{http://brainx.io/}.  The ideas in this proposal are very much a response to the discussions of that meeting.  Moreover, there are already three follow-up meetings scheduled for this calendar year, including a side event at the Unite Nations General Assembly to help the UN i
define grand challenges for global brain sciences.
